House price data in Brunei

### 2024-12-12 manuscript.qmd
Render manuscript

---
title: House price data in Brunei
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: "https://haziqj.ml"
    # note: 
    # roles: writing
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name: Hafeezul Waezz Rabu
    affiliations:
      - ref: ubd
  - name: Amira Barizah Noorosmawie
    affiliations:
      - ref: ubd
  - name: Lutfi Abdul Razak
    affiliations:
      - ref: ubd              
date-modified: last-modified
nocite: |
  @*
abstract: |
  Abstract here.
---

@@

@@

@@

TODO:
- Describe the typical workflow. 
- Describe the LLM data cleaning process.

>>>>

---
title: House price data in Brunei
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: "https://haziqj.ml"
    # note: 
    # roles: writing
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name: Amira Barizah Noorosmawie
    affiliations:
      - ref: ubd        
  - name: Hafeezul Waezz Rabu
    affiliations:
      - ref: ubd
  - name: Lutfi Abdul Razak
    affiliations:
      - ref: ubd              
date-modified: last-modified
nocite: |
  @*
abstract: |
  Abstract here.
---

@@

:::{.column-page}

{{< embed analysis.qmd#tbl-summary >}}

:::

@@

{{< embed analysis.qmd#fig-spatial >}}

{{< embed analysis.qmd#fig-price-evolution >}}

{{< embed analysis.qmd#fig-rppi >}}

@@

TODO:

- Describe the typical workflow. 
- Describe the LLM data cleaning process.

:::{.column-page}

{{< embed analysis.qmd#tbl-avail >}}

:::
